
\begin{appendices}

\section{Hypothesis Test Results}
\label{appendix:hypothesis}
The R Script for running the relevant hypothesis test over the data can be found at the following locations:
\begin{center}

% \begin{table}[h]
\begin{tabular}{|l|l|}
\hline
 Test &  Location\\ \hline
 Number of features &  sentimentAnalysis/statisticalAnalysis/featureSelection.R\\
 Model Selection &  sentimentAnalysis/statisticalAnalysis/modelSelection.R\\
 Sampling Tests &  sentimentAnalysis/statisticalAnalysis/overUnder.R\\ \hline
\end{tabular}
% \end{table}
\end{center}

\section{Project File Structure}

The postman layout for all the HTTP requests, with example responses can be found at:
\\ https://documenter.getpostman.com/view/5563343/S1EJXgL9
\\ 
VERSIONS USED: 
\begin{itemize}
    \item Python 3.6
    \item Node  8.10
\end{itemize}

\subsection{Diss}
Contains dissertation files .tex files.

\subsection{UI}
Contains UI for running the web application.  To run, node.js and Angular.js will need to be installed.
To start, navigate into directory and run "npm start", this will automatically install dependencies as well.
This runs on port 8000.
UI Design files are in the app directory.

\subsection{Sentiment Analysis}

The final files for carrying out the investigations are in the main directory:

\begin{itemize}
    \item dataProcess.py - Formats each datasets with correct labels and for putting the variables into discrete categories
    \item preProcessingandModel.py - Investigating N-Gram / Number of features / Model
    \item overUnderTest.py - Investigating sampling methods
    \item finalModel.py - Contains a copy of the final model
    \item adjustModel.py  - Contains the adjustment model for dealing with the dependencies between the variables.
    \item bagOfWords.py - Runs the lexicon analysis investigation
    \item ./data -  contains the datasets and output statistics for the hypothesis tests
    \item ./FinalGraphs -  contains the output graphs from the investigations
    \item ./oldFiles - contains initial trials into setting up the investigations.
\end{itemize}


\subsection{Sentiment Python Server}

\begin{itemize}
    \item train.py
    \item server.py
\end{itemize}
train.py contains an instance of the final model as set out by the Sentiment Analysis directory finalModel.py and  hosts it on a very simple python server so that it can be accessed by the web app. 
To run the server, navigate into the directory and run "python server.py". Runs on port 8090.

\subsection{Spotify Data}
To start, navigate into directory and run "npm start", this will automatically install dependencies as well.  This will only run if the secrets.js file is accessible. Runs on port 8080.

\subsection{Statistical Analysis}
Contains the R files for running the hypothesis tests set out.

\section{Project Log}

\end{appendices}
