
\section{Introduction}
Analysing the emotions behind a piece of text is not always an easy problem even for human readers, and trying to compute this is much harder. 
Existing sentiment analysis tools primarily concentrate on just whether a text is positive or negative. \cite{kolchyna2015twitter}
Most text that we want to analyse however expresses more emotion than just positivity or negativity, and this project will attempt to use various analysis techniques to analyse input text and produce detailed sentimental feedback about it.

To be able to showcase this work in a meaningful way there will be a web application produced as part of this project, where a user can input text and the sentiment can be used to create an output which is interesting to the user. 
The output planned for the project is to link the calculated sentiment to the users Spotify account, where using their top artists and mood of the text that they input, a playlist can be created for them using songs that they enjoy and are relevant to their current emotion.
To be able to ensure enough emotive text to be entered by the user, questions will need to be posed by the application that result in relatively long answers. For example the question "How are you feeling today?" could just lead to the user responding with one word answers like "good" or "OK". A statement that could be used to evoke a more emotive response would be something like "Please describe how your week is going", which should cause more text to be input.

\input{LitReview/2-similar.tex}
\input{LitReview/3-sentimentStructures.tex}
\input{LitReview/4-availibleData.tex}
\input{LitReview/5-dataProcessing.tex}
\input{LitReview/6-emotionClassification.tex}
\input{LitReview/7-analysis.tex}
\input{LitReview/8-textEntry.tex}


\section{Conclusion}
Due to the research done, there is now a clearer plan for moving forward with this project. Unnecessary parts have been removed, and there is a more specific focus for how the sentiment analysis tool is going to work. 
There is extra time to work on the machine learning side of the project, meaning there is now the opportunity for more experimentation with different methods.

Decisions still need to be made, such as the exact emotion classes from the Emotional Classification Table given by Russell \cite{VADMapping}, but progress is happening and there is a plan of how to move forward from this point.